Kindly Bent to Free Us

### 2019-03-11 kindly/motivation.tex
Start working on the examples.

>>>>

\subsection{A session on linearity}

A classical example of linearity at work are to control the uses of resources such
as files or network handles.
%
Session types, notably, allow to statically type check protocols.
For instance, the type \lstinline{!int.!int.?int.end} represent a session
where the program must send two integers, receive an integer, then end the session.
%
In this context, it is essential that channels
are used linearly, since every use of the channel
will make the protocol progress and change the type of the channel.

Session types are usually defined with the following operators:

\begin{center}
  \begin{tabular}{r l}
    $\tau ? \mathcal S$ & Send a value of type $\tau$ then continue with protocol $S$.\\
    $\tau ? \mathcal S$& Receive a value of type $\tau$ then continue with protocol $S$.\\
    $\mathcal S \oplus \mathcal S'$& Choose between protocols $S$ and $S'$.\\
    $\mathcal S \operatorname{\&} \mathcal S'$& Offer a choice between protocols $S$ and $S'$.
  \end{tabular}
\end{center}

It is well known that binary session types can be embedded into ML languages
\cite{DBLP:journals/jfp/Padovani17}. We can easily
embed session types in our language and provide the following API:

\begin{lstlisting}
type 'S st : lin
val receive: ('a ? 'S) st -> 'a * 'S st
val send : ('a:'k). 'a -> ('a ! 'S) st -{'k}> 'S st
val close : end st -> unit
\end{lstlisting}

\TODO{Explain}

We can then use these primitives to implement a simple addition service.
We do not need any extra linearity annotations in the code: the fact
that the \texttt{st} type is declared as linear is sufficient.
In the case below, \lstinline{add_service} is inferred to be of type
\lstinline{(int ! int ! int ? end) st -> unit}

\begin{lstlisting}
let add_service ep =
  let (x, ep) = receive ep in
  let (y, ep) = receive ep in
  let ep = send (x + y) ep in
  close ep
\end{lstlisting}

% \begin{figure}
%   \centering
%   \begin{lstlisting}
% val select : ('S st -{'k}> 'a) -> 'a ot -{'k}> ('S dual) st
% val branch : 'm it -> 'm
%   \end{lstlisting}
%   \caption{Session primitives}
%   \label{api:session}
% \end{figure}
